Sample-Efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-02 paper/main.tex
Fixed typos

\begin{icmlauthorlist}
\icmlauthor{Aidan Scannell}{aalto,fcai}
\icmlauthor{Arno Solin}{aalto}
\icmlauthor{Joni Pajarinen}{aalto}
% \icmlauthor{Firstname1 Lastname1}{equal,yyy}
% \icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
% \icmlauthor{Firstname3 Lastname3}{comp}
% \icmlauthor{Firstname4 Lastname4}{sch}
% \icmlauthor{Firstname5 Lastname5}{yyy}
% \icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
% \icmlauthor{Firstname7 Lastname7}{comp}
% %\icmlauthor{}{sch}
% \icmlauthor{Firstname8 Lastname8}{sch}
% \icmlauthor{Firstname8 Lastname8}{yyy,comp}
%\icmlauthor{}{sch}
%\icmlauthor{}{sch}
\end{icmlauthorlist}

@@

Reinforcement learning  \citep[RL, \eg][]{sutton2018reinforcement} has shown much promise in games, animation and robotics.
However, applying RL in real-world environments is challenging. The problem is two-fold,
{\em (i)}~handling high dimensional/complex observation spaces is non-trivial, and {\em (ii)}~deep RL typically requires millions of data points which can be unpractical (or costly), \ie it is very sample inefficient.\looseness-1

% Given such a latent space,
% Whilst these latent states are often lower dimensional this is not always
Many approaches have been proposed to improve sample efficiency in deep RL.
As \citet{laskinCURLContrastiveUnsupervised2020} highlighted, these can generally be divided into two streams of research:
{\em (i)} auxillary tasks on the agent's observations and {\em (ii)}~world models that predict the future
\citep{haRecurrentWorldModels2018,hafnerLearning2019,hansenTemporalDifferenceLearning2022}.
In this work, we are interested in the first class of methods, which use auxillary tasks to improve sample efficiency.
In particular, we focus on representation learning methods which compress observations into latent states.
Nevertheless, our representation learning borrows ideas from world models as it uses multi-step predictions in a
latent-space dynamics model to learn temporally consist representations \citep{zhaoSimplifiedTemporalConsistency2023}.
% In particular, methods for compressing observations into latent states.%, aka representation learning.

>>>>

\begin{icmlauthorlist}
\icmlauthor{Aidan Scannell}{aalto,fcai}
\icmlauthor{Kalle Kujanpää}{aalto,fcai}
\icmlauthor{Yi Zhao}{aalto}
\icmlauthor{Arno Solin}{aalto}
\icmlauthor{Joni Pajarinen}{aalto}
% \icmlauthor{Firstname1 Lastname1}{equal,yyy}
% \icmlauthor{Firstname2 Lastname2}{equal,yyy,comp}
% \icmlauthor{Firstname3 Lastname3}{comp}
% \icmlauthor{Firstname4 Lastname4}{sch}
% \icmlauthor{Firstname5 Lastname5}{yyy}
% \icmlauthor{Firstname6 Lastname6}{sch,yyy,comp}
% \icmlauthor{Firstname7 Lastname7}{comp}
% %\icmlauthor{}{sch}
% \icmlauthor{Firstname8 Lastname8}{sch}
% \icmlauthor{Firstname8 Lastname8}{yyy,comp}
%\icmlauthor{}{sch}
%\icmlauthor{}{sch}
\end{icmlauthorlist}

@@

Reinforcement learning  \citep[RL, \eg][]{sutton2018reinforcement} has shown much promise in games, animation, and robotics.
However, applying RL in real-world environments is challenging. The problem is two-fold,
{\em (i)}~handling high dimensional/complex observation spaces is non-trivial, and {\em (ii)}~deep RL typically requires millions of data points which can be unpractical (or costly), \ie it is very sample inefficient.\looseness-1

% Given such a latent space,
% Whilst these latent states are often lower dimensional this is not always
Many approaches have been proposed to improve sample efficiency in deep RL.
As \citet{laskinCURLContrastiveUnsupervised2020} highlighted, these can generally be divided into two streams of research:
{\em (i)} auxiliary tasks on the agent's observations and {\em (ii)}~world models that predict the future
\citep{haRecurrentWorldModels2018,hafnerLearning2019,hansenTemporalDifferenceLearning2022}.
In this work, we are interested in the first class of methods, which use auxiliary tasks to improve sample efficiency.
In particular, we focus on representation learning methods that compress observations into latent states.
Nevertheless, our representation learning borrows ideas from world models as it uses multi-step predictions in a
latent-space dynamics model to learn temporally consistent representations \citep{zhaoSimplifiedTemporalConsistency2023}.
% In particular, methods for compressing observations into latent states.%, aka representation learning.
